Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach

### 2016-08-11 introduction.tex
Ricardo's comments added.

\section{Introduction}
\noindent
This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15). \citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs. Basically, the visibility graph presents the connection between nodes in a network. For any time series, two characteristics are attributed to each event: occurrence time and value of the event. Two events are in connection or visible to each other if no other event interrupts their linear connection. In mathematical form, events $i$ and $j$ are visible to each other if the following equation is fulfilled:

\begin{equation}
\frac{y_i - y_k }{t_k - t_i} > \frac{y_i - y_j}{ t_j - t_i} ,
\end{equation}

@@

where $y$ is the value and $t$ is the time of the event, and $k$ is the index of any event occurring between events  $i$  and  $j$. The visibility graph generated from a time series holds the following conditions: 1) each event is visible to the first event at its right and left side (if there is any) (Connectivity); 2) the algorithm is developed without defining a direction for the links (Undirected); and 3) rescaling or translation of a time series does not change the resulting visibility graph (invariant under affine transformations of the series data) \citep{Lacasa2008}. This concept has applications in fields including geophysical studies. \\

@@

VG method also is applied through considering the timespan between earthquakes. \citet{Telesca2016}   defined    $<T_C>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India. They found that  $<T_C>$  changes through time, indicating that the topological properties of the earthquake network are not stationary. In addition,  $<T_C>$  significantly decrees before the largest shock of the catalog. Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks. 

@@

In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions, namely Azerbaijan (Az), Alborz Mountain Range (Al), and Kopeh Dagh (Ko).  Recently, northern Iran has been studied in detail from different seismological points of view.  \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}. Using the smoothed seismicity method, \citet{Khoshnevis2016} studied the seismic hazard of the three northern tectonic seismic regions. Having a considerable number of recorded earthquakes, extensive seismic history, and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series. Significant aspect of our work includes the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zone. We present the relationship between  $k-M$  slope and $b-value$  in these three tectonic seismic regions. We analyze the sensitivity of the catalogs to the number of events and the threshold magnitude. We also investigate the variation of  $<T_C>$  value through time.

>>>>

\section{Introduction}

@@

This article presents the application of VG method on seismicity of northern Iran using the recorded earthquake during the last 10 years (2005-15). Recent studies show that this period (2005-15) has the most complete catalog especially for small earthquakes $(M < 3)$ \citep[e.g.][]{Khoshnevis2016}.  \citet{Lacasa2008} introduced a simple and fast computational method, known as visibility algorithm, to convert time series into graphs. Basically, the visibility graph presents the connection between nodes in a network. This concept has applications in many fields including geophysical studies\citep[e.g.,][]{Telesca2012_CSF,Long2013,Wang2012}. \\

@@

VG method also is applied through considering the timespan between earthquakes. \citet{Telesca2016}   defined    $<T_c>$  as the parameter window mean interval connectivity time ,  as an indication of the mean linkage time between earthquakes, in studying the 2003-12 earthquake sequence in the Kachchh region of western India. They found that  $<T_C>$  changes through time, indicating that the topological properties of the earthquake network are not stationary. In addition,  $<T_c>$  significantly decrees before the largest shock of the catalog. Analyzing the Gutenberg-Richter values of  the magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series by using the features of networks. 

@@

In this study, we use visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions, namely Azerbaijan (Az), Alborz Mountain Range (Al), and Kopeh Dagh (Ko).  Recently, northern Iran has been studied in detail from different seismological points of view.  \citet{Nemati2015} studied the most recent 200 years of seismicity in northern Iran. The frequency of shocks varied widely, from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years (3.25 event/year) for the Kopeh-Dagh region \citep{Nemati2015}. Using the smoothed seismicity method, \citet{Khoshnevis2016} studied the seismic hazard of the three northern tectonic seismic regions. Having a considerable number of recorded earthquakes, extensive seismic history, and being in a unique tectonic seismic region, northern Iran is a good platform from which to analyze the visibility graph method's capabilities for studying the magnitude time series. Significant aspect of our work includes the compassion of earthquake catalog, conversion of the earthquake magnitude and computation of the completeness magnitude for each tectonic seismic zone. We present the relationship between  $k-M$  slope and $b-value$  in these three tectonic seismic regions. We analyze the sensitivity of the catalogs to the number of events and the threshold magnitude. We also investigate the variation of  $<T_c>$  value through time.

### 2016-08-11 results.tex
Ricardo's comments added.

\noindent
Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions. We categorized magnitudes in small magnitude bins ($\Delta M=0.1$). It is clear from the Fig.~\ref{fig:mag-time} that the specific magnitude bin can result in different connectivity degrees regarding the occurring time of the earthquake event. In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure06.pdf} 
\caption{ $k-M$ relationship for north Iran tectonic seismic regions. The blue circles indicate the connectivity degrees. The red line is the linear regression line fits the data. The numbers on the lines is the slope of the lines.}
\label{fig:k_m_plot_m}
\end{figure}
 \noindent
We compared the  $k-M$  slope with the  $b-value$  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time. The  $b-value$  is generated through the maximum likelihood estimation  \citep{Aki1965} .

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
\end{equation}
 \noindent
where $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region. The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.  \citet{Telesca2013}  studied the effect of the number of earthquakes in the catalog on the  $k-M$  slope. Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.  According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes. The minimum size of random windows is 150 events. (Note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively.). The maximum size is the size of the entire catalog. For each randomly picked magnitude time series,  we estimate $Mc$; then the $k-M$  and $b-value$ are calculated. Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables. Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
\label{fig:random}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure08.pdf} 
\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}. The lines represent the linear regression fit of data. The correlation coefficients (R) are represented for different combination of data.}
\label{fig:regression}
\end{figure}

\noindent
Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time. Having a lower number of events, we chose 20 events as the window length with a shift of one event between two successive windows. The calculated parameters of each window were associated with the time of occurrence of the last event in the sliding window. The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar. In general, in all regions the $b-value$  and  $k-M$  slope drop considerably before large earthquakes. The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
\noindent
\citet{Telesca2016}  observed the decrease in  $<T_C>$  before the large earthquake of the western India earthquake sequence. Fig.\ref{fig:tc}  shows the time variation of  $<T_C>$   in the study area. The reduction of  $<T_C>$   before large earthquakes is clearly visible.  \citet{Telesca2016}  demonstrated that the decrement of  $<T_C>$   before a large earthquake is independent of window size and threshold magnitude. Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure09.pdf} 
\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_C >$ (Right) as a function of time for three tectonic seismic regions in north Iran. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference). Decreasing the value of  $<T_C>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
\label{fig:tc}
\end{figure}

>>>>

\noindent
Fig.~\ref{fig:k_m_plot_m}  shows the  $k-M$  relationship for the study regions. It is clear from the Fig.~\ref{fig:mag-time} that the specific magnitude bin can result in different connectivity degrees regarding the occurring time of the earthquake event. In general, with increasing magnitude, the connectivity degree increases, which increases the slope of the  $k-M$  relationship.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.35]{figures/pdf/Figure07.pdf} 
\caption{ $k-M$ relationship for north Iran tectonic seismic regions. The blue circles indicate the connectivity degrees. The red line is the linear regression line fits the data. The numbers on the lines is the slope of the regression lines.}
\label{fig:k_m_plot_m}
\end{figure}
 \noindent
We compared the  $k-M$  slope with the  $b-value$  of the Gutenberg-Richter law through the entire catalog and in the sliding windows in time. The  $b-value$  is generated through the maximum likelihood estimation  \citep{Aki1965} .

\begin{equation}
b = \frac{log_{10}(e) }{\overline{M} - M_{min}},
\end{equation}
 \noindent
where $e$ is the mathematical constant, $\overline{M}$ is the average magnitude, and  $M_ {min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic region. The number of sequences and threshold magnitudes is considerably different for all tectonic seismic regions.  \citet{Telesca2013}  studied the effect of the number of earthquakes in the catalog on the  $k-M$  slope. Comparing the result with the Guerrero region with reduced random sequence,  \citet{Telesca2013}  found that the number of sequences did not affect the  $k-M$  slope.  According to  \citet{Telesca2012}, the threshold magnitude has minor effect in the VG parameters.\\
\noindent
In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude, we randomly picked 200 sequences from the catalogs with various sequence sizes. Number of events at each sequence should be low enough to be able to choose 200 random sequence from the catalog (note that the number of events in each catalog, before removing the events with magnitude less than the completeness magnitude, is 271, 1262, and 399 for Azerbaijan, Alborz, and Kopeh Dagh regions, respectively). Also it should be long enough to preserve the seismic characteristic of each tectonic seismic region. Based on mentioned criteria, we choose the minimum size of random windows as 150 events. The maximum size is the size of the entire catalog. The random sequences are consecutive, in other words, we randomly determine the initial event and sequence size, then we pick that size of event starting from the initial event. For each randomly picked magnitude time series,  we estimate $Mc$; then the $k-M$  and $b-value$ are calculated. Fig.~\ref{fig:random} shows the relationship between  $k-M$  slope and  $b-value$  of the randomly selected data and the statistical parameters for variables. Although changing the number of events and the threshold magnitude is slightly changing the results, however,  the results are fairly well clustered for each tectonic seismic region.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/Figure08.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic regions for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations in percent $(standard \ deviation / mean)$.}
\label{fig:random}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure09.pdf} 
\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}. The lines represent the linear regression fit of data. The correlation coefficients (R) are represented for different combination of data.}
\label{fig:regression}
\end{figure}

\noindent
Fig.\ref{fig:tc} shows the variation of the  $k-M$  slope and  $b-value$  with time. Due to lower number of events in Azerbaijan's catalog, we choose 20 events as the window length with a shift of one event between two successive windows. With higher window length we loose the variation of considerable amount of information in time (e.g. with n=40 we loose almost half of the Azerbaijan catalog). Due to taking average values of successive windows, very small window length can not display the seismicity behavior especially before big earthquake. Maintaining consistency, we use the window length equal to 20 events for all three regions. The calculated parameters of each window are associated with the time of occurrence of the last event in the sliding window. The  $k-M$  slope and  $b-value$  in all tectonic seismic regions are very similar. In general, in all regions the $b-value$  and  $k-M$  slope drop considerably before large earthquakes. The decline in the  $b-value$  before large earthquakes has been studied in many regions \citep{Wyss2000, Wyss2006, Schorlemmer2005, Chan2012}.
\noindent
\citet{Telesca2016}  observed the decrease in  $<T_c>$  before the large earthquake of the western India earthquake sequence. Fig.\ref{fig:tc}  shows the time variation of  $<T_c>$   in the study area. The reduction of  $<T_c>$   before large earthquakes is clearly visible.  \citet{Telesca2016}  demonstrated that the decrement of  $<T_c>$   before a large earthquake is independent of window size and threshold magnitude. Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions (see Fig.\ref{fig:tc} for reference.)

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure10.pdf} 
\caption{ Variation of $k-M$ slope  and $b-value$ (Left), and $ < T_c >$ (Right) as a function of time for three tectonic seismic regions in north Iran. Black arrows show the occurrence of the major earthquakes. Numbers on arrows indicate the moment magnitude of the earthquake (see Fig.~\ref{fig:mag-time} for reference).  The magnitude-time series are presented as a filled plot blew each plot. The variation of the heigh of filled plots are corresponding to the event magnitudes. Decreasing the value of  $<T_c>$  ,  $k-M$ , and  $b-value$  before large earthquakes predominantly happened in all tectonic seismic regions.}
\label{fig:tc}
\end{figure}

### 2016-08-11 seismicity.tex
Ricardo's comments added.

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure01.pdf} 
\caption{Region of interest and tectonic seismic regions. At the top, the map of Iran and surrounding countries is presented. The study area is located in the gray box. At the bottom, the study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure02.pdf} 
\caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
\label{fig:faults}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
\caption{Declustered instrumental seismicity map (2005 - 2015) of northern Iran. Different colors indicate the seismicity of different regions. Size of symbols are proportional to the magnitude of the events.}
\label{fig:seismicity}
\end{figure}

\subsection{Catalog Completeness}
\noindent
Catalog completeness is an important factor in studying an earthquake sequence. This characteristic measured as the minimum magnitude of complete recording for earthquake catalog. The completeness magnitude $(M_c)$ is often determined using simple numerical analysis. Two common approaches are maximum curvature method and (MAXC) and goodness-of-fit test (GFT)(see \citet{Wiemer2000}). We use the Goodness-of-fit test and compute $M_c$ for each region's catalog. According to the GFT method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process in order to calculate the goodness of fit for each magnitude.  \citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select the completeness of the catalog. However,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} shows the goodness-of-fit values for three tectonic seismic regions. For each tectonic seismic region, we select the magnitude corresponding to the highest goodness of fit or the first magnitude with the goodness of fit greater than 90\%.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure04.pdf} 
\caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period. The symbols indicate the computed GFT values as function of the earthquake magnitude. The horizontal dashed line indicates the desired threshold for the goodness of fit value at 90 percent.}
\label{fig:completeness}
\end{figure} 
\noindent
Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions. Earthquakes with magnitude greater than the completeness magnitude are represented.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.8]{figures/pdf/Figure05.pdf} 
\caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time. The figure only represents the declustered events greater than minimum magnitude. The 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes are clearly visible as maximum values in Azerbaijan (Az),  Alborz (Az), and Kopeh Dagh (Ko) magnitude-time series.}
\label{fig:mag-time}
\end{figure}

>>>>

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure02.pdf} 
\caption{Region of interest and tectonic seismic regions. At the top, the map of Iran and surrounding countries is presented. The study area is located in the gray box. At the bottom, the study area containing seismotectonic provinces after \citet{Mirzaei1998} is presented. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure03.pdf} 
\caption{Main fault line and fault system in the region of interest. The borderlines of the seismic zones shown in Fig.~\ref{fig:study_region} are shown in background in gray.}
\label{fig:faults}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=1]{figures/pdf/Figure04.pdf} 
\caption{Declustered instrumental seismicity map (2005 - 2015) of northern Iran. Different colors indicate the seismicity of different regions. Size of symbols are proportional to the magnitude of the events.}
\label{fig:seismicity}
\end{figure}

\subsection{Catalog Completeness}
\noindent
Catalog completeness is an important factor in studying an earthquake sequence. This characteristic measured as the minimum magnitude of complete recording for earthquake catalog. The completeness magnitude $(M_c)$ is often determined using simple numerical analysis. Two common approaches are maximum curvature method (MAXC) and goodness-of-fit test (GFT)(see \citet{Wiemer2000}). We use the Goodness-of-fit test and compute $M_c$ for each region's catalog. According to the GFT method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for selecting the completeness magnitude for each catalog include: 1) calculating the a-  and  b-  value based on minimum magnitude; 2) generating  synthetic events based on the achieved value when the cumulative number of events obey the power law distribution; and 3) calculating goodness of fit for predicted and observed cumulative numbers for each magnitude bin  \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process in order to calculate the goodness of fit for each magnitude.  \citet{Wiemer2000} assumed a goodness of fit of 90\% as a threshold to select the completeness of the catalog. However,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} shows the goodness-of-fit values for three tectonic seismic regions. For each tectonic seismic region, we select the magnitude corresponding to the highest goodness of fit or the first magnitude with the goodness of fit greater than 90\%.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure05.pdf} 
\caption{ Selection of completeness magnitude $M_c$ of the three tectonic seismic regions in northern Iran in 2005-15 period. The symbols indicate the computed GFT values as function of the earthquake magnitude. The horizontal dashed line indicates the desired threshold for the goodness of fit value at 90 percent. The vertical dashed lines indicate the completeness magnitude of each tectonic seismic region.}
\label{fig:completeness}
\end{figure} 
\noindent
Based on the results represented in Fig.~\ref{fig:completeness}, we select the minimum magnitudes for complete recording,  $M_c$ , is 3.5, 2.6, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time}  shows the magnitude time series of the declustered data for the three regions. Earthquakes with magnitude greater than the completeness magnitude are represented.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.8]{figures/pdf/Figure06.pdf} 
\caption{Variation of moment magnitude ($M_w$) of 2005-2015 earthquake for north Iran as a function of time. The figure only represents the declustered events greater than minimum magnitude. The 2012 $M_w 6.4$ East Azerbaijan, 2010 $M_w 5.8$ Damghan, and 2012 $M_w 5.4$ Neyshabur earthquakes are clearly visible as maximum values in Azerbaijan (Az),  Alborz (Az), and Kopeh Dagh (Ko) magnitude-time series.}
\label{fig:mag-time}
\end{figure}
